---
title: "Quantitative Management Modeling - Assignment_3"
output:
  pdf_document: default
  html_notebook: default
---



```{r}
library("lpSolveAPI")
library("lpSolve")
library("tinytex")

#Creating a table representing the data
unit.shipping.cost<- matrix(c(22,14,30,600,100,
                 16,20,24,625,120,
                 80,60,70,"-","-"), ncol=5,byrow=T)
colnames(unit.shipping.cost) <- c("Warehouse1", "Warehouse2",      "Warehouse3", "ProductionCost", 
"ProductionCapacity")
rownames(unit.shipping.cost) <- c("PlantA", "PlantB", "Demand")
unit.shipping.cost <- as.table(unit.shipping.cost)
unit.shipping.cost


```

#The objective function is to minimize the transportation cost

$$ Z = 622X_{11} + 614X_{12} + 630X_{13} + 0X_{14} + 641X_{21} + 645X_{22} + 649X_{23} + 0X_{24}$$
#Subject to the following constraints

$${\text Supply \hspace{3mm} Constraints}$$
$$X_{11} + X_{12} + X_{13} + X_{14} <= 100$$
$$X_{21} + X_{22} + X_{23} + X_{24} <= 120$$
$${\text Demand \hspace{3mm} Constraints}$$
$$X_{11} + X_{21}>= 80$$
$$X_{12} + X_{22}>= 60$$
$$X_{13} + X_{23}>= 70$$
$$X_{14} + X_{24}>= 10$$
$${\text  Non - Negativity \hspace{3mm} Constraints} $$
$$X_{ij} >= 0 \hspace{3mm} \text {Where i = 1,2 and j = 1,2,3,4} $$
```{r}
#As the demand is not equal to supply we are creating the dummy variables .
#Creating a matrix for the given objective function
transport_cost <- matrix(c(622,614,630,0,
                 641,645,649,0), ncol=4, byrow=T)
transport_cost
#Defining the column names
colnames(transport_cost) <- c("Warehouse1", "Warehouse2",
                              "Warehouse3", "Dummy")
#Defining the row names, row signs and row values 
rownames(transport_cost) <- c("PlantA", "PlantB")
transport_cost
row_signs <- rep("<=",2)
row_RHS <- c(100,120)
#It cannot be greater to the specified units as it is the supply function.

#Defining the column signs and column values
col_signs <- rep(">=",4)
col_RHS <- c(80,60,70,10)
#It can be greater than the specified units as it is the demand function.
```

```{r}
#Running the lp.transport function 
lp_transport_cost <- lp.transport(transport_cost,"min", row_signs,row_RHS,col_signs,col_RHS)
```

```{r}
#Getting the objective value
lp_transport_cost$objval
```

#The resulting minimization value is $132,790***, which is the lowest total cost that can be derived from the costs of production and shipping of defibrillators.

```{r}
#Getting the constraints value
lp_transport_cost$solution
```

#80 AEDs in Plant B - Warehouse1, 60 AEDs in Plant A - Warehouse2, 40 AEDsin Plant A - Warehouse3, 30 AEDs*** in Plant B - Warehouse3 should be produced in each plant and then distributed to each of the three wholesaler warehouses in order to minimize the overall cost of production as well as shipping.

#Formulate the dual of the above transportation problem.

#Since the primal was to minimize the transportation cost the dual of it would be to maximize the value added(VA).

$$ {\text Maximize \hspace{3mm} VA = } \hspace{3mm} 80W_1 + 60W_2 + 70W_3 - 100P_A - 120P_B$$

#Subject to the following constraints

$$ {\text Total \hspace{3mm} Payments \hspace{3mm} Constraints} $$
$$ W_1 - P_A >= 622 $$
$$ W_2 - P_A >= 614$$
$$ W_3 - P_A >= 630$$
$$ W_1 - P_B >= 641$$
$$ W_2 - P_B >= 645$$
$$ W_3 - P_B >= 649$$
$${\text Where \hspace{3mm} W_1 = Warehouse \hspace{3mm} 1}$$
$$\hspace{3mm} W_2 = Warehouse \hspace{3mm} 2$$
$$\hspace{3mm} W_3 = Warehouse \hspace{3mm} 3$$
$$\hspace{3mm} P_1 = Plant \hspace{3mm} 1$$
$$\hspace{3mm} P_2 = Plant \hspace{3mm} 2$$

#Economic Interpretation of the dual
$$W_1 <= 622 + P_A $$
$$W_2 <= 614 + P_A $$
$$W_3 <= 630 + P_A $$
$$W_1 <= 641 + P_B$$
$$W_2 <= 645 + P_B$$
$$W_3 <= 649 + P_B$$

$$ \text It \hspace{3mm}is \hspace{3mm} clear\hspace{3mm} from \hspace{3mm} the \hspace{3mm} above \hspace{3mm} that \hspace{3mm} W_1 - P_A >= 622, \hspace{3mm} can \hspace{3mm} be \hspace{3mm} exponented \hspace{3mm} as \hspace{3mm} W_1 <= 622 + P_A$$


$$ \text In \hspace{3mm} this \hspace{3mm} case \hspace{3mm} W1 \hspace{3mm} is \hspace{3mm} taken \hspace{3mm} into \hspace{3mm} account \hspace{3mm} as \hspace{3mm} payments \hspace{3mm} made \hspace{3mm} at \hspace{3mm} the \hspace{3mm} source \hspace{3mm}$$
$$which \hspace{3mm} is \hspace{3mm} nothing \hspace{3mm} but \hspace{3mm} the \hspace{3mm} revenue \hspace{3mm}$$
$$Whereas\hspace{3mm} P_A + 622 \hspace{3mm} is \hspace{3mm} the \hspace{3mm} money \hspace{3mm} paid \hspace{3mm} at \hspace{3mm} the \hspace{3mm} origin \hspace{3mm} at \hspace{3mm} Plant_A \hspace{3mm}$$ 

$$\text Hence \hspace{3mm} the \hspace{3mm} equation \hspace{3mm} is \hspace{3mm} MR_1 >= MC_1.$$

$$\text For \hspace{3mm} profit \hspace{3mm} maximization, \hspace{3mm} the \hspace{3mm} Marginal \hspace{3mm} revenue \hspace{3mm} should \hspace{3mm}be \hspace{3mm}$$
$$equal\hspace{3mm} to\hspace{3mm} Marginal \hspace{3mm} cost.\text Therefore,\hspace{3mm}MR_1 = MC_1$$

$$\text Therefore\hspace{3mm} it\hspace{3mm} can\hspace{3mm} be \hspace{3mm} concluded \hspace{3mm} that,$$
$$Profit\hspace{3mm} maximization\hspace{3mm} takes\hspace{3mm} place \hspace{3mm} if\hspace{3mm} MC\hspace{3mm} is\hspace{3mm} equal\hspace{3mm} to\hspace{3mm} MR.$$
#If MR > MC, we will need to increase the production supply to meet the Marginal Revenue and if MR < MC we will have to decrease the cost at plants in order to meet the Marginal Revenue (MR).

