---
title: "Final Project"
author: "Bharath Chennu, Michael Geist, Elmy Luka"
date: "2011-12-11"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<style>
table {
  font-family: arial, sans-serif;
  border-collapse: collapse;
  width: 100%;
}

td, th {
  border: 1px solid #dddddd;
  text-align: left;
  padding: 8px;
}

tr:nth-child(even) {
  background-color: #dddddd;
}
</style>


<html>
<head>
<title>Final Project</title>
</head>
<body>
<p>Objective : You have been tasked with the objective of forming groups. Assume that your class consists of 12 students, and you would like to form 4 groups of 3 students each. Your primary objective is to ensure that you maximize the chance that each group will do well on a class project. Here are the requirements to form groups:<br>
1.Each group should have exactly 3 students<br>
2.The objective is to maximize the chance of success for each group on a class project<br>
Before you can solve this problem, there are several issues that must be addressed. Some of these being:<br> 
What factors affect the success of groups? Define three factors, e.g., GPA, gender, etc., that you feel affect the contributions that students make towards project success. <br> 
How do the above factors combine to define success? For example, is a person with high GPA the same as one with a more relevant background? Decide on how each of the factors contribute toward your definition of success.<br> 
How will you collect data for these factors? For this assignment, randomly generate sensible data for each of the above three defined factors.<br>  
What are your decision variables? <br> 
What is your objective function? <br> 
What are your constraints? <br> 
Formulate and solve the problem. Provide the corresponding R markdown file, and a narrative recorded presentation justifying your approach to the choice of factors, data collection, and formulation. <br> 
</p><br>

<p>
So the first thing we did is we wanted to make a table of data  Within excel we used the RAND function and INT(RAND()*(a specific number))  That randomly generated data is being display below.<br>
<table>
<tr><th>Student</th><th>GPA</th><th>Attendance</th><th>Current Course Grade</th></tr>
<tr><td>1</td><td>2.23</td><td>20</td><td>85</td></tr>
<tr><td>2</td><td>2.18</td><td>25</td><td>56</td></tr>
<tr><td>3</td><td>1.92</td><td>6</td><td>69</td></tr>
<tr><td>4</td><td>3.49</td><td>11</td><td>93</td></tr>
<tr><td>5</td><td>2.87</td><td>17</td><td>78</td></tr>
<tr><td>6</td><td>1.92</td><td>24</td><td>72</td></tr>
<tr><td>7</td><td>2.09</td><td>23</td><td>80</td></tr>
<tr><td>8</td><td>2.06</td><td>14</td><td>64</td></tr>
<tr><td>9</td><td>3.18</td><td>12</td><td>85</td></tr>
<tr><td>10</td><td>3.98</td><td>24</td><td>89</td></tr>
<tr><td>11</td><td>2.49</td><td>16</td><td>97</td></tr>
<tr><td>12</td><td>4.00</td><td>20</td><td>88</td></tr>
</table>
</p>
The three different variables we picked were GPA, Attendance, and then Course Grade.<br>
GPA is between 0 and 4.  The higher the number the the better the student grade would be.<br>
Attendance is based on 25 classes.<br>
Course Grade is based on 100 percent to 50 percent(We made the assumption that if they were below 50 they would have withdrew from class).<br>
We also made sure that the number presented by the random number generator within excel would make sense.  Someone with a 4.00 GPA would not have a 50 percent in the class (most often).  As long as it made sense we left it alone.
</p><br>
<p>
Now we want to formulate the problem.<br>
Objective Function<br><br>
$$Max Z = 85\sum_{i=1}^{4} x_{i1} + 56\sum_{i=1}^{4} x_{i2} + 69\sum_{i=1}^{4} x_{i3} + 93\sum_{i=1}^{4} x_{i4} + 78\sum_{i=1}^{4} x_{i5} + 72\sum_{i=1}^{4} x_{i6} + 80\sum_{i=1}^{4} x_{i7} + 64\sum_{i=1}^{4} x_{i8} + 85\sum_{i=1}^{4} x_{i9} + 89\sum_{i=1}^{4} x_{i10} + 97\sum_{i=1}^{4} x_{i11} + 88\sum_{i=1}^{4} x_{i11}$$<br>
<br>
You can see that we are using the grades of each person along with the summation of i being the number of groups.<br>
<br>
Our Objective Function comes with the following constants:<br>
Constraint for Groups<br>
$$\sum_{j=1}^{12} x_{ij}$$ where i= groups (1-4) and j=Students (1-12)<br><br>
Constraint for GPA<br>
$$\sum_{j=1}^{12}GPA_j x_{ij}>=12$$ where i= groups (1-4) and j=Students (1-12)<br><br>
Constraint for Attendance<br>
$$\sum_{j=1}^{12}ATT_j x_{ij}>=75$$ where i= groups (1-4) and j=Students (1-12)<br><br>
Constraint to only assign a student to one group<br>
$$\sum_{i=1}^{4}x_{ij}=1$$ where i= groups (1-4) and j=Students (1-12)<br><br>
All $$x_{ij}$$ are positive intergers i=1-4 and j=1-12<br>

```{r}
library(lpSolve)
library(lpSolveAPI)
data <- data.frame(Person = c(1:12),
                        GPA = c(2.23, 2.18, 1.92, 3.49, 2.87, 1.92, 2.09, 2.06, 3.18, 3.98, 2.49, 4.00),
                        Attendence = c(20,25,6,11,17,24,23,14,12,24,16,10),
                        ClassGrade = c(85,56,69,93,78,72,80,64,85,89,97,88))
#make linear programming object
lp <- make.lp(0,48)
#setting as integer 
set.type(lp, 48, "integer")
set.objfn(lp, rep(c(85,56,69,93,78,72,80,64,85,89,97,88,
                    85,56,69,93,78,72,80,64,85,89,97,88,
                    85,56,69,93,78,72,80,64,85,89,97,88,
                    85,56,69,93,78,72,80,64,85,89,97,88)))
#setting the LP to be a maximization
lp.control(lp, sense="max")
#adding the constraint for the groups to be formed (3 people per group)
add.constraint(lp, c(rep(1,12),rep(0,36)), "=", 3)
add.constraint(lp, c(rep(0,12),rep(1,12),rep(0,24)), "=", 3)
add.constraint(lp, c(rep(0,24),rep(1,12),rep(0,12)), "=", 3)
add.constraint(lp, c(rep(0,36),rep(1,12)), "=", 3)
#Adding the GPA constraint (no one can have higher than 4.00*3 people =12)
add.constraint(lp, rep(data$GPA,4), ">=", 12)
#Adding attendance constraints (no one could have come to class more than 25 times * 3 people = 75)
add.constraint(lp, rep(data$Attendence,4), ">=", 75)
#Making sure that each student is counted 1 time so that student could not be added too multiple groups
add.constraint(lp, rep(c(1,rep(0,11)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,1),1,rep(0,10)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,2),1,rep(0,9)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,3),1,rep(0,8)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,4),1,rep(0,7)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,5),1,rep(0,6)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,6),1,rep(0,5)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,7),1,rep(0,4)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,8),1,rep(0,3)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,9),1,rep(0,2)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,10),1,rep(0,1)),4), "=", 1)
add.constraint(lp, rep(c(rep(0,11),1),4), "=", 1)
solve(lp)
get.objective(lp)
get.variables(lp)
data1 <- data.frame(Person = c(1:12),
                    GPA = c(2.23, 2.18, 1.92, 3.49, 2.87, 1.92, 2.09, 2.06, 3.18, 3.98, 2.49, 4.00),
                    Attendence = c(20,25,6,11,17,24,23,14,12,24,16,10),
                    ClassGrade = c(85,56,69,93,78,72,80,64,85,89,97,88),
                    Group = c(2,2,4,3,3,1,1,4,4,1,2,3))
data1



```
</body>